---
title: "Custom link styles"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In getting started you saw what the built-in styling looks like (both the default and the alternative). In this article you'll see how to disable the built-in styling and specify your own.

## Setup

Initialize Wikipedia Preview *without styles* by including the following inline code anywhere in your R Markdown document:

````{verbatim}
`r wikipediapreview::wp_init(with_styles = FALSE)`
````

`r wikipediapreview::wp_init(with_styles = FALSE)`

**Note**: If you prefer to have a designated chunk instead of inline code, you can initialize by including the following chunk:

````{verbatim}
```{r wp-init, results='asis', echo=FALSE}
wikipediapreview::wp_init(with_styles = FALSE)
```
````

Then you can define your own `wiki` CSS class from scratch, rather than overriding any built-in rules:

```{css}
.wiki {
    text-decoration: none;
    color: #0645ad;
    border-bottom: 1px dashed #0645ad;
}
```

## Example

**Source**:

```
You can link to [Wikipedia](https://www.wikipedia.org/) and
you can link to the article about
[Wikipedia](https://en.wikipedia.org/wiki/Wikipedia){.wiki}
```

**Output**:

You can link to [Wikipedia](https://www.wikipedia.org/) and
you can link to the article about
[Wikipedia](https://en.wikipedia.org/wiki/Wikipedia){.wiki}

## Further reading

To learn more about writing CSS, refer to [blogdown: Creating Websites with R Markdown](https://bookdown.org/yihui/blogdown/css.html) (2021) by Yihui Xie, Amber Thomas, Alison Presmanes Hill.
